Coherent optical association of a single molecule

### 2020-10-11 paper.tex
white space, regenerate pdf
Update figure 4 legend
update numbers

% For a weakly bound molecular state, the spacing between states is generally smaller compared to deeply bound states and thus limits the maximum usable detuning and therefore the effectiveness of the scattering reduction by increasing the detuning.
%Furthermore, due to similarity in wavefunction size, the weakly bound molecular ground state and initial atomic state have strong coupling with the atomic excited state which contributes significantly to the total scattering rate. The rate of such a scattering process is proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold, and thus can also be made smaller by detuning away from the dissociation threshold.
% (Should we also mention scattering of the atomic initial state too? This should affect the Raman process as well)

@@

%\textcolor{blue}{Main point here. Small $\Omega_a/\Omega_m$ ratio can be compensated by larger detuning, but Stark shift is problematic.} \textcolor{red}{KW: I agree Stark shift limitation is definitely pretty problematic, but I would also argue that larger detuning may not be able to save the day, because of the many vibrational states in a molecular potential, the lower Raman rabi frequency which results from detuning farther and possibly running into other limitations if you have to do that, such as the background off resonant scattering rate from near threshold states or technical background scattering.} \textcolor{blue}{yes, I agree. I want to layout the structure .... motivate for the better ratio first, than talk about choosing the state.} \textcolor{red}{KW: Okay, got it. Makes sense. }
%In addition to the intermediate state, the choice of the initial and final states is also critical. 

@@

%Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.  

@@

First we look at the change in resonance frequency.
As a function of the tweezer power, we observe a linear dependency on the resonance frequency
caused by the differential light shift between the atomic and molecular state (Fig.~\ref{f-det}A).
When we vary the tweezer frequency around the $v'=0$ excited state,
we can further observe a $1/\delta$ component and a constant component
in the experimentally explored region.
The background is caused by coupling to other excited states that are further away in energy.
The $1/\delta$ component, however, is predominantly due to the coupling between
the molecular state and the $v'=0$ excited state.
From this measurement, we can calculate a matrix element between the molecular state and
the excited state, $\Omega_m$, of $2\pi\times89.40(17) \mathrm{MHz}/\sqrt{\mathrm{mW}}$
or $2\pi\times346.24(65) \mathrm{MHz}$ for the $15 \mathrm{mW}$ tweezer power used above.
This number is about $3$ times larger than the value of
$2\pi\times27 \mathrm{MHz}/\sqrt{\mathrm{mW}}$ \todo{ref/sm theory}.
\todo{make sure theory part mentions $\Omega_{down}\gg\Omega_{up}$,
  also $\Omega$ vs $\Omega'$ for the single leg vs cross coupling number.}

In order to calculate the matrix element ratio,
next we discuss the dependencies of the Raman Rabi frequency.
The Raman Rabi frequency shows a non-linear dependency on the tweezer power due to the change
in the atomic wavefunction caused by the change in confinement (Fig.~\ref{f-det}B).
The atomic matrix element, $\Omega_a$,
is proportional to the the short range atomic wavefunction amplitude,
which scales as $P^{0.375}$ for weakly interacting particles.
However, due to the strong interaction between the two atoms, this approximation breaks down.
Instead, theory calculation shows that the scaling is very well approximated by $P^{0.29}$
within the range of confinement in our experiment.
Combined with the intensity factor, the Raman Rabi frequency should scale with $P^{1.29}$,
which agrees with our experimental result.
Similar to the light shift, there is also an offset and
a $v'=0$ component in the Raman Rabi frequency.
Based on the $v'=0$ component and the $\Omega_m$ measured above,
we measured a up leg Rabi frequency of $...$, or $...$ at $15 \mathrm{mW}$ tweezer power.
This gives a Rabi frequency, and therefore matrix element, ratio of $...$,
which is in fact better than the theory prediction of $...$
and should not cause the scattering from the $v'=0$ state to be higher than expected.

Unfortunately, the offset in the Raman Rabi frequency fit cancels
the Rabi frequency for red detuning Raman transition and reduces it by about $...\times$
at the current detuning. However, this difference is not enough to explain
the difference we observed in the experiment.
The same offset will increase the Rabi frequency for blue detuning
but we have observed additional excited states at slightly higher frequencies
which prevent the blue side of the transition to be usuable for Raman transition.

\begin{figure*}
  \includegraphics[height=4.5cm]{fig4.pdf}
  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
    (A) The light shift of the Raman resonance scales as $P_{tweezer}$
    and follows $1/\delta$ with an offset.
    (B) Raman Rabi frequency scales as $P_{tweezer}^{1.29}$ and follows $1/\delta$ with an offset.
    From these results we can confirm the theory prediction of
    the atom-molecule matrix element ratio.
    (C) Atomic scattering rate scales as $P_{tweezer}^{2.58}$,
    this is consistent with a two photon scattering process.
    We have not measured a clear dependency of the loss rate on the tweezer detuning.
    \label{f-det}}
\end{figure*}

>>>>

% For a weakly bound molecular state, the spacing between states is generally smaller compared to deeply bound states and thus limits the maximum usable detuning and therefore the effectiveness of the scattering reduction by increasing the detuning.
% Furthermore, due to similarity in wavefunction size, the weakly bound molecular ground state and initial atomic state have strong coupling with the atomic excited state which contributes significantly to the total scattering rate. The rate of such a scattering process is proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold, and thus can also be made smaller by detuning away from the dissociation threshold.
% (Should we also mention scattering of the atomic initial state too? This should affect the Raman process as well)

@@

% \textcolor{blue}{Main point here. Small $\Omega_a/\Omega_m$ ratio can be compensated by larger detuning, but Stark shift is problematic.} \textcolor{red}{KW: I agree Stark shift limitation is definitely pretty problematic, but I would also argue that larger detuning may not be able to save the day, because of the many vibrational states in a molecular potential, the lower Raman rabi frequency which results from detuning farther and possibly running into other limitations if you have to do that, such as the background off resonant scattering rate from near threshold states or technical background scattering.} \textcolor{blue}{yes, I agree. I want to layout the structure .... motivate for the better ratio first, than talk about choosing the state.} \textcolor{red}{KW: Okay, got it. Makes sense. }
% In addition to the intermediate state, the choice of the initial and final states is also critical.

@@

% Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.

@@

First we look at the change in resonance frequency.
As a function of the tweezer power, we observe a linear dependency on the resonance frequency
caused by the differential light shift between the atomic and molecular state (Fig.~\ref{f-det}A).
When we vary the tweezer frequency around the $v'=0$ excited state,
we can further observe a $1/\delta$ component and a constant component
in the experimentally explored region.
The background is caused by coupling to other excited states that are further away in energy.
The $1/\delta$ component, however, is predominantly due to the coupling between
the molecular state and the $v'=0$ excited state.
From this measurement, we can calculate a matrix element between the molecular state and
the excited state, $\Omega_m$, of $2\pi\times36.162(20) \mathrm{MHz}/\sqrt{\mathrm{mW}}$
or $2\pi\times140.056(78) \mathrm{MHz}$ for the $15 \mathrm{mW}$ tweezer power used above.
This number is consistent with the value of
$2\pi\times27 \mathrm{MHz}/\sqrt{\mathrm{mW}}$ \todo{ref/sm theory}.
\todo{make sure theory part mentions $\Omega_{down}\gg\Omega_{up}$,
  also $\Omega$ vs $\Omega'$ for the single leg vs cross coupling number.}

In order to calculate the matrix element ratio,
next we discuss the dependencies of the Raman Rabi frequency.
The Raman Rabi frequency shows a non-linear dependency on the tweezer power due to the change
in the atomic wavefunction caused by the change in confinement (Fig.~\ref{f-det}B).
The atomic matrix element, $\Omega_a$,
is proportional to the the short range atomic wavefunction amplitude,
which scales as $P^{0.375}$ for weakly interacting particles.
However, due to the strong interaction between the two atoms, this approximation breaks down.
Instead, theory calculation shows that the scaling is very well approximated by $P^{0.29}$
within the range of confinement in our experiment.
Combined with the intensity factor, the Raman Rabi frequency should scale with $P^{1.29}$,
which agrees with our experimental result.
Similar to the light shift, there is also an offset and
a $v'=0$ component in the Raman Rabi frequency.
The $v'=0$ component of the Raman Rabi frequency is
$2\pi\times161.8(22) \mathrm{Hz\cdot mW^{-1.29}}$,
or $2\pi5.324(73)\mathrm{kHz}$ at $15 \mathrm{mW}$ tweezer power.
Together with the $\Omega_m$ measured above, the up leg Rabi frequency is
$2\pi11.53(16)\mathrm{MHz}$.
This gives a Rabi frequency, and therefore matrix element, ratio of $12.14(16)$,
which is in fact better than the theory prediction of $23.7$
and should not cause the scattering from the $v'=0$ state to be higher than expected.

Unfortunately, the offset in the Raman Rabi frequency fit cancels
the Rabi frequency for red detuning Raman transition and reduces it by about $30\%$
at the current detuning. However, this difference is not enough to explain
the difference we observed in the experiment.
The same offset will increase the Rabi frequency for blue detuning
but we have observed additional excited states at slightly higher frequencies
which prevent the blue side of the transition to be usuable for Raman transition.

\begin{figure*}
  \includegraphics[height=4.5cm]{fig4.pdf}
  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
    (A) The light shift of the Raman resonance scales as $P_{tweezer}$
    and follows $1/\delta$ with an offset.
    The fit also includes a small term that is proportional to $P_{tweezer}^2$
    which is caused by the effective magnetic field generated by the tweezer which is
    perpendicular to the real magnetic field.
    (B) Raman Rabi frequency scales as $P_{tweezer}^{1.29}$ and follows $1/\delta$ with an offset.
    From these results we can confirm the theory prediction of
    the atom-molecule matrix element ratio.
    (C) Atomic scattering rate scales as $P_{tweezer}^{2.58}$,
    this is consistent with a two photon scattering process.
    We have not measured a clear dependency of the loss rate on the tweezer detuning.
    \label{f-det}}
\end{figure*}
